---
title: "`crosstalk` Tutorial"
output: 
    html_document:
      toc: true
      toc_float: true
      theme: cosmo
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, error = FALSE, out.width = "100%")
```

```{r pkg-load}
library(dplyr)
library(ggplot2)
library(plotly)
library(DT)
library(leaflet)
library(crosstalk)
library(checkdown)
```

```{r data-load}
trips <- 
  readRDS("trips_apr.rds") %>%
  select(station_name, station_id, year_2019, pct_change, prop_wend_2019) %>%
  mutate_at(vars(pct_change, prop_wend_2019), round, 2)
stations <- readRDS("stations.rds")
```

## Motivation

This tutorial will help you learn to use the `crosstalk` package to link different `htmlwidgets`. After completing this tutorial, you will be able to build an application like the one below, which visualizes the number of rides at a sample of Chicago train stations in 2019 versus 2020. 

Click and drag a subset of points on the scatterplot below to see how the map and table are dynamically filtered.

```{r full-example, out.width = "80%"}

# create SharedData ----
trips_ct <- SharedData$new(trips, key = ~station_id, group = "loc")
trips_sub_ct <- SharedData$new(trips[,c("station_name", "station_id", "pct_change")], 
                               key = ~station_id, group = "loc")

# create individual widgets ----

# map

# table
dt <- datatable(trips_sub_ct,
                fillContainer = TRUE,
                rownames = FALSE,
                colnames = c("Station", "ID", "% Change"),
                options = list(autowidth = TRUE))

# plot
gg <- ggplot(trips_ct) +
    aes(
      x = prop_wend_2019, 
      y = pct_change,
      col = pct_change,
      name = station_name) +
    geom_point() +
    guides(col = FALSE) +
  labs(
    x = "% Apr 2019 Trips on Weekend",
    y = "% Change Apr 2020 vs 2019"
  ) +
  scale_x_continuous(labels = scales::percent) +
  scale_y_continuous(labels = scales::percent)
gg_ly <- 
  ggplotly(gg, tooltip = "name") %>%
  highlight(on = "plotly_selected",
            off = "plotly_doubleclick")

# create final output ----
bscols(gg_ly,  dt, widths = c(6, 6))
```

```{r}
rm(list = ls())
trips <- 
  readRDS("trips_apr.rds") %>%
  select(station_name, station_id, year_2019, pct_change, prop_wend_2019) %>%
  mutate_at(vars(pct_change, prop_wend_2019), round, 2)

# make SharedData object ----
trips_ct <- SharedData$new(trips, key = ~station_id)

# make ggplots using SharedData object ----
gg_year <-
  ggplot(trips_ct) +
  aes(x = year_2019, y = pct_change, col = pct_change) +
  geom_point()

# make htmlwidgets ----
gg_year_ly <- ggplotly(gg_year)
dt_stations <- datatable(trips_ct)

# compose output ----
bscols(gg_year_ly,
dt_stations)
```


```{r}
rm(list = ls())
d1 <- data.frame(
  idnumeric = 1:length(letters),
  id = letters,
  x = rnorm(length(letters)),
  y = runif(length(letters)))

d1shared <- SharedData$new(d1, key = ~id )
d1table <- datatable(d1shared)

p1plot <- ggplot(d1shared) + aes(x = x,y = y) + geom_point()
pp1plot_p <- ggplotly(p1plot) 

#pp1plot_p <- plotly::plot_ly(d1shared, x = ~x ,y = ~y) |> add_markers() |> highlight("plotly_click")
#pp2plot_p <- plotly::plot_ly(d1shared, x = ~x ,y = ~y) 
bscols(pp1plot_p, d1table)


```





